Results (Julia)

### 2024-11-04 notebooks/01_results_julia.qmd
update

fs = temp_plot(wind_df).([maps1, maps2])
fnames = ["wind_distribution_time", "wind_sw_paramters"]
easy_save.(fnames, fs) .|> display;
```

```{julia}
let df = jno_df # let df = j_events_taus
    fs = temp_plot(df; color=r_map).([maps1, maps2])
    fnames = ["juno_distribution_r", "juno_sw_paramters"]
    easy_save.(fnames, fs)
    display.(fs)
end;
```

>>>>

let df = wind_df, fnames = ["wind_distribution_time", "wind_sw_paramters"]
    fs = temp_plot(df).([maps1, maps2])
    easy_save.(fnames, fs)
    display.(fs)
end
```

```{julia}
# let df = j_events_taus
let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
    fs = temp_plot(df; color).([maps1, maps2])
    easy_save.(fnames, fs)
    display.(fs)
end
```
